Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-04 workflow/workflow.Rmd
start investigating infinite values in norm. values

```{r parallel, echo=FALSE}
runZinb <- TRUE
runClus <- TRUE
NCORES <- 6
mysystem = Sys.info()[["sysname"]]
if (mysystem == "Darwin"){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == "Linux"){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print("Please change this to allow parallel computing")
  register(SerialParam())
}
```

@@

```{r zinb}
print(system.time(se <- zinbwave(core, K = 50, X = "~ Batch",
                                 residuals = TRUE,
                                 normalizedValues = TRUE)))
```

@@

[DR: Fanny, did you figure out why we get infinite values? If not, we need to at least explain why we are doing what we do below.]

>>>>

```{r parallel, echo=FALSE}
NCORES <- 2
mysystem = Sys.info()[["sysname"]]
if (mysystem == "Darwin"){
  registerDoParallel(NCORES)
  register(DoparParam())
}else if (mysystem == "Linux"){
  register(bpstart(MulticoreParam(workers=NCORES)))
}else{
  print("Please change this to allow parallel computing")
  register(SerialParam())
}
```

@@

```{r zinb}
print(system.time(se <- zinbwave(core, K = 40, X = "~ Batch",  
                                 residuals = TRUE,
                                 normalizedValues = TRUE)))
```

@@

[DR: Fanny, did you figure out why we get infinite values? If not, we need to at least explain why we are doing what we do below.]
[FP: I tried to play with the epsilon to see if we could get rid of the infinite values in the normalized values. With default epsilon, we have about 40 infinite values, with epsilon 10000, we have about 20. When K = 0, there is no infinite values but the normalized values don't capture as much of biology (looking at the pca with published clusters colors). It seems to me that we get infinite norm. values when the number of parameters to estimate is large. I tried to reduce K to 25 (no infinite but W not as good), 40 (infinite values but W looks ok)... to be continued.]
